Predicting Tags for StackOverflow Posts

### 2013-06-19 stackExchange/writeups/iccm-2013/writeup.tex
foo
Former-commit-id: c782536a5292b72da82c3c108b419f1ed421bc0d [formerly 83c11cfce91a3b642b29d1fcbea1aa2deb7c624b]
Former-commit-id: e422b3b2bb063633fb21499ae73d17e6d4e7fb03

ACT-R's declarative memory retrieval process is the core of the StackOverflow model.
This is a more constrained and cognitively-plausible model than the set of machine learning techniques used by \citeA{Kuo2011} for the same task. 
Interestingly, when using ACT-R's retrieval mechanism, the model performs significantly better than the less constrained models in \citeA{Kuo2011}.
So there is no reason to think that people do not engage in a process much like this to select tags.
However, more research is necessary before making the strong claim that the StackOverflow model \emph{is} the process people go through when selecting tags.
In particular, the tag errors made by authors should be looked at, and model behavior should be tested against these important counter examples.
Also, places where the StackOverflow model deviate from ACT-R's default retrieval theory (i.e., the offset term, entropy and attentional weighting) should be looked at in greater detail.

>>>>

ACT-R's declarative memory retrieval process makes up the core of the StackOverflow model.
This is a more constrained and cognitively-plausible model than the set of machine learning techniques used by \citeA{Kuo2011} for the same task. 
Interestingly, when using ACT-R's retrieval mechanism, the model performs significantly better than the less constrained models in \citeA{Kuo2011}.
So there is no reason to think that people do not engage in a process much like this to select tags.
However, more research is necessary before making the strong claim that the StackOverflow model \emph{is} the process people go through when selecting tags on the site, or tags in general.
In particular, the tag errors made by authors should be looked at, and model behavior should be tested against these important counter examples.
Also, places where the StackOverflow model deviates from ACT-R's default retrieval theory (i.e., the offset term, entropy and attentional weighting) should be looked at in greater detail.
